THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-22 DishReflectometry/Paper1_v1.tex

Since it was first proposed in \citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal \citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; \citealt{XXX}),
(BIGHORNS; \citealt{XXX}),
(SARAS; \citealt{patra_et_al2014}),
(SCIHI; \citealt{voytek_et_al2014}),
(HyPerion; \citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; \citealt{XXX}),
the Murchison Widefield Array (MWA; \citealt{XXX}),
the Giant Metre-wave Radio Telescop (GMRT; \citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; \citealt{XXX}),
and the future Square Kilometre Array (SKA; \citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

One of the most problematic effects facing these experiments is instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
contaminating spectral modes that might
otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
a telescope's response scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another.

A major step forward for the field of 21~cm cosmology has been the development
of a mathematical description of telescope chromaticity, how it varies with
element separation (or telescope diameter), and what it implies for distinguishing
foreground emission from the cosmological 21~cm signal \citep{XXX}.  The ``wedge'', as it is
colloquially known, describes a linear relationship between the separation between elements
in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
a flat sky, and using appropriate
cosmological scalars,
the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
$\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
spectral axis $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
within the limits of the wedge,
foreground contamination may be suppressed through a combination of calibration and model 
subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
the chromaticity of the elements in isolation from the chromaticity inherent to
element separation in an interferometric baseline.}.  In promising avoidance-based
foreground strategy employed by PAPER \citep{parsons_et_al2014,ali_et_al2015}, these modes
may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.

In this paper, we examine the performance of a new prototype HERA element in the context of
this new wedge-based framework.  In coordination with \citet{XXXsisterpapers}, we compare 
reflectometry measurements with
a specification for the spectral performance of an element, given models of the relative brightness of
foreground and 21~cm reionization modes in $k$-space.  
% XXX document map

The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\
The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Reflectometry measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering a feed after
$n^{th}$ reflection off the feed and the dish is:

@@

Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantlu reduces the system response higher delays.  

@@

\bibliographystyle{apj}
\bibliography{biblio.bib}
\end{document}

>>>>

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise ~\citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; ~\citealt{XXX}),
(BIGHORNS; ~\citealt{XXX}),
(SARAS; ~\citealt{patra_et_al2014}),
(SCIHI; ~\citealt{voytek_et_al2014}),
(HYPERION; ~\citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescop (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

One of the most problematic effects facing these experiments is instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
contaminating spectral modes that might
otherwise be used to measure reionization ~\citep{XXX}.  Moreover, the chromaticity of
a telescope's response scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another.

A major step forward for the field of 21~cm cosmology has been the development
of a mathematical description of telescope chromaticity, how it varies with
element separation (or telescope diameter), and what it implies for distinguishing
foreground emission from the cosmological 21~cm signal ~\citep{XXX}.  The ``wedge'', as it is
colloquially known, describes a linear relationship between the separation between elements
in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
a flat sky, and using appropriate
cosmological scalars,
the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
$\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
spectral axis $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
within the limits of the wedge,
foreground contamination may be suppressed through a combination of calibration and model 
subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
~\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
the chromaticity of the elements in isolation from the chromaticity inherent to
element separation in an interferometric baseline.}.  In promising avoidance-based
foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.

In this paper, we examine the performance of a new prototype HERA element in the context of
this new wedge-based framework.  In coordination with ~\citet{XXXsisterpapers}, we compare 
reflectometry measurements with
a specification for the spectral performance of an element, given models of the relative brightness of
foreground and 21~cm reionization modes in $k$-space.  
% XXX document map

The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  ~\citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

@@

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{eqnarray}
\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
\label{eq3}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain. The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas. Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures. Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.

@@

 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\
The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed ~\citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter ~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Reflectometry measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering a feed after
$n^{th}$ reflection off the feed and the dish is:

@@

Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  

@@

\bibliography{biblio.bib}{}
\bibliographystyle{apj}
\end{document}
